\section{Scope}
	\label{sec:Scope}
	
	Given the brief introduction and overview of software objectives, the following scope defines the requirements elicited:
	\newline
	

	\vspace{-2mm}
	\subsection{Scope Disclaimer}
		
		The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL NOT", "SHOULD", "SHOULD NOT", "RECOMMENDED",  "MAY", and
		"OPTIONAL" in this document are to be interpreted as described in RFC 2119.
		\newline

	\vspace{-2mm}
	\subsection{Scope Statement}
		
		The intent of this project is to provide a Linux port of the Windows Group Policy Object (GPO) editor and a means 
		to deploy these policies to a multitude of ‘Gnu’s not Unix’ (GNU) systems through a common non-ambiguous domain specific 
		language (DSL). 
		\newline

	\vspace{-2mm}
	\subsection{Scoped Objectives}
	
		\large{\bfseries{Client Server Model}}
		
		\vspace{2mm}
		\normalsize
		{		
			Centralised management being the theme of this project establishes the inception of the concept of a central
			authority and therein a client server model.  The implementation is REQUIRED to provide a client-server model 
			that MUST exhibit the following.

			\begin{enumerate}[itemsep=1pt,parsep=1pt]
				\item 	The implementation MUST support at least two variants of Linux to prove applicability.
				\item 	The design MUST support the ability to be extended to support a multitude of different systems 
						with varying revisions of supporting packages. 
				\item 	The implementation SHOULD use the Practical Extraction and Reporting Language (PERL) for highest availability possible. 
				\item 	The server is REQUIRED to scale from two test clients to hundreds of clients.
				\item   This SHOULD be achieved via the Master Slave Design Pattern or similar pattern.  
				\item   A master with multiple slave servers implementation is RECOMMENDED. 
				\item 	A compiled language MUST NOT be used as updates to the client SHALL be sent via the server which will 
						deployed on varying architectures.
				\item   The Server SHOULD support both Push and Pull; at least MUST implement support for pull requests.
			\end{enumerate}
		}

		\large{\bfseries{Domain Specific Language}}
		
		\vspace{2mm}
		\normalsize
		{	
			The domain specific language should exhibit the following characteristics.

				\begin{enumerate}[itemsep=1pt,parsep=1pt]
					\item 	The domain specific language MUST be extensible.
					\item 	As new modules SHALL be deployed to the client, these Modules MAY provides hooks to the interpreter which it MUST accept.
					\item 	The Domain Specific Language(DSL) SHOULD be a implemented as a hybrid language.
					\begin{itemize}
						\item 	The interpreter SHALL parse the Domain Specific Language(DSL) and process it.
						\item 	The interpreter SHALL execute embedded general purpose language instructions defined in the Client server model.
					\end{itemize}
				\end{enumerate} 
		}
		
		\large{\bfseries{Directory Services Schema}}

		\vspace{2mm}
		\normalsize
		{	
			The directory services schema MUST provide a means of representing and storing the following elements.

				\begin{enumerate}[itemsep=1pt,parsep=1pt]
					\item 	Files, Permissions, Lvalue and Rvalue of elements within configuration files.
					\item 	Services and with common names, which MUST be translated by the client into the distribution specific names.
					\item 	A representation organisational groups in hierarchy fashion compared to active directory MUST be implemented.
					\item 	Computer objects SHALL be recognised by a globally unique identifier (GUID) represented as a 32-character hexadecimal string. 
				\end{enumerate}
		}
		
		\large{\bfseries{Administrator Front End}}
		
		\vspace{2mm}
		\normalsize
		{				
			The Administrator Group Policy editor should exhibit the following characteristics. 

				\begin{enumerate}[itemsep=1pt,parsep=1pt]
					\item 	MUST provide the ability of creating organisational units.
					\item 	MUST provide the ability to move computers between organisational units.
					\item 	MUST Implement a hierarchy of organisational units where by policies MAY be inherited and overrides where applicable.
					\item 	MUST provide a means to modify policies.
					\item 	On application or change of a policy the server MUST generate new domain specific language script.
					\item 	The front end MUST provide a means of importing existing policies in the form of the Domain Specific Language(DSL).
					\item 	The User Interface SHOULD implement the ability to push updates to the client.
				\end{enumerate}
		}	
